### 2020-06-08 docs/ICTT2019/RMethod_ictt26.tex

\graphicspath{{figures/}}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%   BEGIN DOCUMENT
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

@@

@@

After computing the numerical solution of the diffusion problem by finite differences without corrections at the cell interfaces, we evaluate new current estimates by using escape, transmission and reflection probabilities according to the given geometry type, as derived from the integral equation in section \ref{sec:ce}. Then, the solution by the Ronen method is sought iteratively as explained in section \ref{sec:impl}. Anderson acceleration through the DAAREM algorithm is also used during the iteration process \cite{henderson2019damped}, reducing considerably the number of iterations to achieve residuals on the relative flux differences below $10^{-6}$. Its use is crucial to find the fixed point solution throughout the non-linear iterations of the RM.

>>>>

\graphicspath{{figures/}}

% The lineno packages adds line numbers. Start line numbering with
% \begin{linenumbers}, end it with \end{linenumbers}. Or switch it
% on for the whole article with \linenumbers.
\usepackage[modulo]{lineno}
% \linenumbers
% \modulolinenumbers[5]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%   BEGIN DOCUMENT
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}

@@

\linenumbers

@@

After computing the numerical solution of the diffusion problem by finite differences without corrections at the cell interfaces, we evaluate new current estimates by using escape, transmission and reflection probabilities according to the given geometry type, as derived from the integral equation in section \ref{sec:ce}. Then, the solution by the Ronen method is sought iteratively as explained in section \ref{sec:impl}. Anderson acceleration through the DAAREM algorithm (Damped Anderson Acceleration with Epsilon Monotonicity) is also used during the iteration process \cite{henderson2019damped}, reducing considerably the number of iterations to achieve residuals on the relative flux differences below $10^{-6}$. Its use is crucial to find the fixed point solution throughout the non-linear iterations of the RM.
